\documentclass[letterpaper,10pt]{moderncv}
\moderncvstyle{casual} % Style options: 'casual' (default), 'classic', 'oldstyle', 'banking'
\moderncvcolor{blue}   % Color options: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey', 'black'

\usepackage[scale=0.85]{geometry} % Adjust margins
\setlength{\hintscolumnwidth}{3cm} % Width of the timeline on your left

\name{Sam}{Sullivan}
\title{Student | Fullstack Developer}
\email{mail@samsullivan.dev}
\social[github]{samsullivandelgobbo}

\begin{document}

\makecvtitle

\section{Objective}
Versatile Fullstack Developer and Neuroscience student with a background in aviation and IT consultancy. Known for delivering high-quality web solutions and rapidly adapting to new technologies. Experienced in managing large-scale APIs and developing custom web applications.

\section{Education}
\cventry{Expected Graduation 2026}{Bachelor of Science in Neuroscience}{University of Toronto}{}{}{Pursuing a degree in Neuroscience, focusing on integrating scientific knowledge into technology development.}

\section{Experience}
\cventry{2022--Present}{Fullstack Developer}{Salesy}{\href{https://salesy.ca}{Salesy.ca}}{}{
    \begin{itemize}
        \item Created a comprehensive digital platform for automotive dealerships, integrating live inventory into user interfaces.
        \item Led the development of adaptive chatbots and customizable web suites.
    \end{itemize}
}
\cventry{In Development}{Fullstack Developer}{Cardog}{}{}{
    \begin{itemize}
        \item Developing a platform to simplify car buying by aggregating dealership inventories.
        \item Building a scalable and efficient API for inventory management.
    \end{itemize}
}
\cventry{2023--Present}{Fullstack Developer}{Canadian Chinchilla Rescue}{\href{https://canadianchinchilla.ca}{CanadianChinchilla.ca}}{}{
    \begin{itemize}
        \item Developed a dynamic management platform and e-commerce solution.
        \item Facilitated website transition to a more scalable and robust system.
    \end{itemize}
}
\cventry{2019--2021}{IT Consultant}{Newmarket Hyundai}{}{}{
    \begin{itemize}
        \item Provided IT consultancy services, focusing on networking and server deployment.
        \item Enhanced the dealership's IT infrastructure for improved operational efficiency.
    \end{itemize}
}

\section{Skills \& Technologies}
\cvitem{Web Development \& API Management}{Expertise in Svelte, React, Next.js, package building, browser testing.}
\cvitem{Database \& Cloud Technologies}{Skilled in database management and cloud infrastructure automation (Vercel, Digital Ocean).}
\cvitem{Custom Solution Development}{Developed a custom VIN decoder and comprehensive web applications.}
\cvitem{Web Design \& UX}{Adherence to design guidelines, experience in creating custom component libraries.}

\section{Certifications}
\cvitem{Commercial Helicopter Pilot License}{Certified commercial helicopter pilot with comprehensive training in aviation.}
\newpage



\section{Projects}
\cvitem{Salesy (2022--Present)}{A digital infrastructure platform for automotive dealerships.}
\cvitem{Cardog \\ (In Development)}{A platform in development to streamline car buying by consolidating dealership inventories.}




\section{Skills \& Technologies}
\subsection{Web Development}
\cvitem{Frameworks}{Svelte, Sveltekit, React, Next.js}
\cvitem{Integrations}{Shopify, Stripe, Plaid}
\cvitem{Package Building}{UMD, npm, pnpm}
\cvitem{Testing}{Browser Testing with Playwright}

\subsection{DevOps}
\cvitem{Cloud Infrastructure}{Automation, Vercel, Digital Ocean, GCP, AWS, Azure}

\subsection{Web Design}
\cvitem{Design Standards}{Adherence to strict design guidelines (vehicle manufacturers)}
\cvitem{Component Libraries}{Creation of custom component libraries}

\subsection{Web Scraping}
\cvitem{Techniques}{Browser Automation, Headless Scraping, Traditional Scraping}
\cvitem{Systems}{Setup and management of comprehensive scraping pipelines}

\subsection{AI UX Development}
\cvitem{OpenAI}{Integration of OpenAI functions}
\cvitem{Databases}{Experience with Vector Databases}
\cvitem{Billing}{Implementation of usage billing systems}

\subsection{Database Management}
\cvitem{Database Systems}{PostgreSQL, MS SQL Server}



\section{References}
Available upon request.

\end{document}

